Work Stress

### 2023-03-17 outputs/paper/paper.qmd
Update paper to include changes on survey

# Appendix
## Appendix A: Supplementary Survey
There are many researchers finding way to reduce work stress for everyone, and finding the major causes that is making people to face work stress.

@@

1.  What is your age?
    a. 18-24
    b. 25-34
    c. 35-44
    d. 45-64
    e. 65+
2.  What is your gender?
    a. Male
    b. Female
    c. Others
    d. Prefer not to say
3.  Which causes do you think is the main cause of you facing work stress?
    a. Traffic delays
    b. Too much work tasks
    c. Long hours
    d. Not interested in the job
    e. Others
4.  How many hours do you prefer to work for the week?
    a. 25 and under hours
    b. 26-30 hours
    c. 31-35 hours
    d. 36-40 hours
5.  How many hours would you work in a entire shift for the day?
    a. 4-6 hours
    b. 7-8 hours
    c. 9-10 hours
    d. 11-12 hours
6.  How often do you get stress at work?
    a. Always
    b. Most of the times
    c. Sometimes
    d. Few times
    e. Never
7.  How long does it take for you to commute to work?
    a. 15-20 mins
    b. 30 mins
    c. 1 hour 
    d. More than 1 hour
8.  Does your boss or manager make you to work on a lots of tasks on a single work shift?
    a. Yes
    b. Sometimes
    c. Never
    d. Not Applicable

>>>>

# Appendix
## Appendix A: Supplementary Survey

Supplementary Survey is on Google Forms: https://forms.gle/fdPuTeWRb7M68Z8ZA

### Survey Introduction

There are many researchers finding way to reduce work stress for everyone, and finding the major causes that is making people to face work stress.

@@

### Survey Questions

1.  What is your age?
    a. 18-24
    b. 25-34
    c. 35-44
    d. 45-64
    e. 65+
2.  What is your gender?
    a. Male
    b. Female
    c. Prefer not to say
    d. Other...
3.  Which causes do you think is the main cause of you facing work stress?
    a. Traffic delays
    b. Too much work tasks
    c. Long hours
    d. Not interested in the job
    e. Other...
4.  How many hours do you prefer to work for the week?
    a. 25 and under hours
    b. 26-30 hours
    c. 31-35 hours
    d. 36-40 hours
    e. Other...
5.  How many hours would you work in a entire shift for the day?
    a. 4-6 hours
    b. 7-8 hours
    c. 9-10 hours
    d. 11-12 hours
6.  How often do you get stress at work?
    a. Always
    b. Most of the times
    c. Sometimes
    d. Few times
    e. Never
7.  How long does it take for you to commute to work?
    a. 15-20 mins
    b. 30 mins
    c. 1 hour 
    d. More than 1 hour
8.  Does your boss or manager make you to work on a lots of tasks on a single work shift?
    a. Yes
    b. Sometimes
    c. Never
    d. Not Applicable

### Survey Conclusion
